--- 
title: "Lymphoma Treatment 2022"
author: "Jeff Cromwell PhD"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: book
bibliography: [book.bib, packages.bib]
# url: your book url like https://bookdown.org/yihui/bookdown
cover-image:
description: |
  This book is about Lymphoma Treatments.
link-citations: yes
github-repo: rstudio/bookdown-demo
---

# A Compendium of Mathematical Models for Germinal-Center Diffuse Large B Cell Lymphoma 

```{r setup, include=FALSE} 
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
```


```{r tab01, tidy=FALSE,echo=FALSE}
library(DT)
df1<-as.data.frame(read.csv("csv-germinalce-set.csv"))
matchingList <- c("ï..PMID", "Title")
df2 <- df1[, which((names(df1) %in% matchingList)==TRUE)]
datatable(df2, options = list(pageLength = 25))
```


## Monoclonal antibodies 

```{r tab02, tidy=FALSE,echo=FALSE}
library(DT)
df1<-as.data.frame(read.csv("csv-monoclonal-set.csv"))
matchingList <- c("ï..PMID", "Title")
df2 <- df1[, which((names(df1) %in% matchingList)==TRUE)]
df3<-head(df2,4000)
datatable(df3, options = list(pageLength = 25))
```

## RCHOP

```{r tab03, tidy=FALSE,echo=FALSE}
library(DT)
df1<-as.data.frame(read.csv("csv-RCHOPlymph-set.csv"))
matchingList <- c("ï..PMID", "Title")
df2 <- df1[, which((names(df1) %in% matchingList)==TRUE)]
df3<-head(df2,4000)
datatable(df3, options = list(pageLength = 25))
```

```{r, eval=FALSE}
bookdown::render_book()
```

## Radiation and Radio Therapy

```{r eval=FALSE}
bookdown::serve_book()
```

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```

```{r tab05, tidy=FALSE,echo=FALSE}
library(DT)
df1<-as.data.frame(read.csv("csv-radiationt-set.csv"))
matchingList <- c("ï..PMID", "Title")
df2 <- df1[, which((names(df1) %in% matchingList)==TRUE)]
df3<-head(df2,4000)
datatable(df3, options = list(pageLength = 25))
```

## Medicinal Plants

```{r tab04, tidy=FALSE,echo=FALSE}
library(DT)
df1<-as.data.frame(read.csv("csv-medicinalp-set.csv"))
matchingList <- c("ï..PMID", "Title")
df2 <- df1[, which((names(df1) %in% matchingList)==TRUE)]
datatable(df2, options = list(pageLength = 25))
```

<!--chapter:end:index.Rmd-->

# RCHOP

## Rituximab

```{r tab2, tidy=FALSE,echo=FALSE}
library(DT)
df1<-as.data.frame(read.csv("PubChem_pubmed_text_Rituximab target genes.csv"))
matchingList <- c("ï..pmid", "articletitle")
df2 <- df1[, which((names(df1) %in% matchingList)==TRUE)]
df3<-head(df2,4000)
datatable(df3, options = list(pageLength = 25))
```

## Vincristine

```{r tab3, tidy=FALSE,echo=FALSE}
library(DT)
df1<-as.data.frame(read.csv("PubChem_pubmed_text_Vincristine target genes.csv"))
matchingList <- c("ï..pmid", "articletitle")
df2 <- df1[, which((names(df1) %in% matchingList)==TRUE)]
df3<-head(df2,4000)
datatable(df3, options = list(pageLength = 25))
```

## Doxorubicin

```{r tab4, tidy=FALSE,echo=FALSE}
library(DT)
df1<-as.data.frame(read.csv("PubChem_pubmed_text_Doxorubicin target genes.csv"))
matchingList <- c("ï..pmid", "articletitle")
df2 <- df1[, which((names(df1) %in% matchingList)==TRUE)]
df3<-head(df2,4000)
datatable(df3, options = list(pageLength = 25))
```

## Cyclophosphamide

```{r tab5, tidy=FALSE,echo=FALSE}
library(DT)
df1<-as.data.frame(read.csv("PubChem_pubmed_text_Cyclophosphamide target genes.csv"))
matchingList <- c("ï..pmid", "articletitle")
df2 <- df1[, which((names(df1) %in% matchingList)==TRUE)]
df3<-head(df2,4000)
datatable(df3, options = list(pageLength = 25))
```

## Prednisone

```{r tab6, tidy=FALSE,echo=FALSE}
library(DT)
df1<-as.data.frame(read.csv("PubChem_pubmed_text_Prednisone target genes.csv"))
matchingList <- c("ï..pmid", "articletitle")
df2 <- df1[, which((names(df1) %in% matchingList)==TRUE)]
df3<-head(df2,4000)
datatable(df3, options = list(pageLength = 25))
```

<!--chapter:end:01-intro.Rmd-->

# Radiation Treatment {#cross}

```{r tab30, tidy=FALSE,echo=FALSE}
library(DT)
df1<-as.data.frame(read.csv("csv-radiationt-set.csv"))
matchingList <- c("ï..PMID", "Title")
df2 <- df1[, which((names(df1) %in% matchingList)==TRUE)]
#df3<-head(df2,4000)
datatable(df2, options = list(pageLength = 25))
```

## Dose

```{r tab31, tidy=FALSE,echo=FALSE}
library(DT)
df1<-as.data.frame(read.csv("csv-radiationd-set.csv"))
matchingList <- c("ï..PMID", "Title")
df2 <- df1[, which((names(df1) %in% matchingList)==TRUE)]
df3<-head(df2,4000)
datatable(df3, options = list(pageLength = 25))
```


## Sickness


```{r tab32, tidy=FALSE,echo=FALSE}
library(DT)
df1<-as.data.frame(read.csv("csv-radiations-set.csv"))
matchingList <- c("ï..PMID", "Title")
df2 <- df1[, which((names(df1) %in% matchingList)==TRUE)]
df3<-head(df2,4000)
datatable(df3, options = list(pageLength = 25))
```

<!--chapter:end:02-cross-refs.Rmd-->

# Radio Therapy



```{r tab40, tidy=FALSE,echo=FALSE}
library(DT)
df1<-as.data.frame(read.csv("csv-radiothera-set.csv"))
matchingList <- c("ï..PMID", "Title")
df2 <- df1[, which((names(df1) %in% matchingList)==TRUE)]
df3<-head(df2,4000)
datatable(df3, options = list(pageLength = 25))
```


<!--chapter:end:03-parts.Rmd-->

# Lymphatic System


```{r tab70, tidy=FALSE,echo=FALSE}
library(DT)

df1<-as.data.frame(read.csv("csv-LymphaticS-set.csv"))
matchingList <- c("ï..PMID", "Title")
df2 <- df1[, which((names(df1) %in% matchingList)==TRUE)]
df3<-head(df2,4000)
datatable(df3, options = list(pageLength = 25))
```

## Lymph Nodes

```{r tab71, tidy=FALSE,echo=FALSE}
library(DT)
df1<-as.data.frame(read.csv("csv-LymphNodel-set.csv"))
matchingList <- c("ï..PMID", "Title")
df2 <- df1[, which((names(df1) %in% matchingList)==TRUE)]
df3<-head(df2,4000)
datatable(df3, options = list(pageLength = 25))
```

## Lymph


```{r tab72, tidy=FALSE,echo=FALSE}
library(DT)
df1<-as.data.frame(read.csv("csv-Lymphlymph-set.csv"))
matchingList <- c("ï..PMID", "Title")
df2 <- df1[, which((names(df1) %in% matchingList)==TRUE)]
df3<-head(df2,4000)
datatable(df3, options = list(pageLength = 25))
```

<!--chapter:end:04-citations.Rmd-->

# Total Blood Count


```{r tab80, tidy=FALSE,echo=FALSE}
library(DT)
df1<-as.data.frame(read.csv("csv-TotalBlood-set.csv"))
matchingList <- c("ï..PMID", "Title")
df2 <- df1[, which((names(df1) %in% matchingList)==TRUE)]
df3<-head(df2,4000)
datatable(df3, options = list(pageLength = 25))
```

## Lymphocytes


```{r tab81, tidy=FALSE,echo=FALSE}
library(DT)
df1<-as.data.frame(read.csv("csv-Lymphocyte-set.csv"))
matchingList <- c("ï..PMID", "Title")
df2 <- df1[, which((names(df1) %in% matchingList)==TRUE)]
df3<-head(df2,4000)
datatable(df3, options = list(pageLength = 25))
```


## Genomics


```{r tab83, tidy=FALSE,echo=FALSE}
library(DT)
df1<-as.data.frame(read.csv("csv-genomicsly-set.csv"))
matchingList <- c("ï..PMID", "Title")
df2 <- df1[, which((names(df1) %in% matchingList)==TRUE)]
df3<-head(df2,4000)
datatable(df3, options = list(pageLength = 25))
```

<!--chapter:end:05-blocks.Rmd-->

# Compendium Of Mathematical Models

```{r setup2, include=FALSE} 
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
```
For more information consider the new book schedule for release in October 2022 entitled, A Compendium of Mathematical Models for Germinal-Center Diffuse Large B Cell Lymphoma Volume 1 by Jeff Cromwell, PhD

## Additional Titles 

Please visit the Mathematical Learning Space Research Portfolio for additional books at mathlearningspace.weebly.com and the instagram page at mathmusicbiology. 

<!--chapter:end:06-share.Rmd-->

`r if (knitr::is_html_output()) '
# References {-}
'`

<!--chapter:end:07-references.Rmd-->

